A quantitative framework for investigating the reliability of network construction: supplemental information

### 2018-03-21 manuscript/CI_interactions.tex
more reviewers, funding, affiliation change

\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1\ddagger}$, Tomas Roslin$^{2,3\star}$, Kate Wootton$^{2\diamond}$, Dominique Gravel$^{4\triangleright}$}
\date{\begin{minipage}[h]{0.45\textwidth}
\small$^1$ Department of Physics,\\
Chemistry and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
$^2$ Department of Ecology\\ 
P.O. Box 7044\\ 
Swedish University of Agricultural Sciences \\ 
SE-750 07 Uppsala, Sweden 
\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.45\textwidth}
\small$^3$ Spatial Foodweb Ecology Group\\ 
Department of Agricultural Sciences \\ 
PO Box 27 (Latokartanonkaari 5)\\ 
FI-00014 University of Helsinki, Finland\\
$^4$ D\'{e}partement de biologie\\ 
Universit\'{e} de Sherbrooke\\ 
Sherbrooke, Canada
\end{minipage}
}

@@

\vspace{-.25in}
\begin{minipage}[h]{0.25\textwidth}
\small$^\dagger$ Corresponding author:\\
alyssa.cirtwill@gmail.com\\
tel: +46 723 158464
\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.22\textwidth}
\small$^\ddagger$ anna.eklof@liu.se\\
$^\star$ tomas.roslin@slu.se
\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.38\textwidth}
\small$^\diamond$ kate.wootton@slu.se\\
$^\triangleright$ dominique.gravel@usherbrooke.ca
\end{minipage}

@@

  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript. We also thank K\'{e}vin Cazalles for providing feedback on the manuscript.

>>>>

\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1\ddagger}$, Tomas Roslin$^{2\star}$, Kate Wootton$^{2\diamond}$, Dominique Gravel$^{3\triangleright}$}
\date{\begin{minipage}[h]{0.45\textwidth}
\small$^1$ Department of Physics,\\
Chemistry and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
$^2$ Department of Ecology\\ 
P.O. Box 7044\\ 
Swedish University of Agricultural Sciences \\ 
SE-750 07 Uppsala, Sweden\\
$^3$ D\'{e}partement de biologie\\ 
Universit\'{e} de Sherbrooke\\ 
Sherbrooke, Canada
\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.45\textwidth}
\small$^\dagger$ Corresponding author:\\
alyssa.cirtwill@gmail.com\\
tel: +46 723 158464\\
$^\ddagger$ anna.eklof@liu.se\\
$^\star$ tomas.roslin@slu.se\\
$^\diamond$ kate.wootton@slu.se\\
$^\triangleright$ dominique.gravel@usherbrooke.ca
\end{minipage}
}

@@

\vspace{-.4in}

@@

  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript. We also thank K\'{e}vin Cazalles for providing feedback on the manuscript. The authors also appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR). Additional funding was provided by a Formas grant (\#942-2015-1262) to AE.

### 2018-03-21 manuscript/coverletter.tex
more reviewers, funding, affiliation change

    The present work is outstandingly novel relative to the recent work by one of the authors (Tomas Roslin) cited in this manuscript. Kopelke \emph{et al.} (2017) is the data paper describing the \emph{Salix}-galler-parasitoid system used for the quantitative analyses in the present work. Kopelke \emph{et al.} (2017) does not contain any analyses and so does not affect the novelty of the present work in any way.

@@

% Pedro Jordano pedroj@me.com Estacion Biologica de Donana CSIC
% Phillip Staniczenko pstaniczenko@sesync.org National Socio-Environmental Synthesis Center (SESYNC)

>>>>

    The present work uses empirical material published as a data paper by one of the authors (Tomas Roslin). The cited paper, Kopelke \emph{et al.} (2017), presents the extremely high-quality dataset used in the present work but does not contain any analyses. As such, the present work is an entirely novel use of these data, which are also available to the full ecological community.

@@

% Pedro Jordano pedroj@me.com Estacion Biologica de Donana CSIC
% Phillip Staniczenko pstaniczenko@sesync.org National Socio-Environmental Synthesis Center (SESYNC) 
% Louis-Félix Bersier louis-felix.bersier@unifr.ch Université de Fribourg

% Extra suggestion
% Jacopo Grilli jgrilli@santafe.edu Santa Fe Institute
% Eve McDonald-Madden e.mcdonaldmadden@uq.edu.au University of Queensland

% Ben Weinstein Oregon State University weinsteb@oregonstate.edu
% Jean-Philippe Lessard Concordia University jp.lessard@concordia.ca
% Catherine Graham catherine.graham@wsl.ch Swiss Federal Research Institute WSL 
% Anne Chao chao@stat.nthu.edu.tw National Tsing Hua University
% Robert Colwell robertkcolwell@gmail.com Museum of Natural History, University of Colorado Boulder

### 2018-03-21 manuscript/supplemental.tex
more reviewers, funding, affiliation change

\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2,3}$, Kate Wootton$^{2}$, Dominique Gravel$^{4}$}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip $^2$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
\medskip $^3$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
\medskip$^4$ D\'{e}partement de biologie\\ 
Universit\'{e} de Sherbrooke\\ 
Sherbrooke, Canada\\ 
\medskip
$^\dagger$ Corresponding author:\\
alyssa.cirtwill@gmail.com\\
+46 723 158464\\
}
\renewcommand\Authands{ and }

@@

    \bibliographystyle{ecollett} 
    \bibliography{MyCollection}

>>>>

\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2}$, Kate Wootton$^{2}$, Dominique Gravel$^{3}$}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip $^2$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
\medskip$^3$ D\'{e}partement de biologie\\ 
Universit\'{e} de Sherbrooke\\ 
Sherbrooke, Canada\\ 
\medskip
$^\dagger$ Corresponding author:\\
alyssa.cirtwill@gmail.com\\
+46 723 158464\\
}
\renewcommand\Authands{ and }

@@

    \bibliographystyle{ecol_let} 
    \bibliography{manual_abbrev}
